\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
Figures~\ref{fig:homoheleshaw_VN3} and \ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively. At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed. Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region. However, formation of fingers can be readily noticed at early stages of the simulation conducted with {\it VR}=10.

>>>>

\medskip
Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively. At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed. Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region. However, formation of fingers can be readily noticed at early stages of the simulation conducted with {\it VR}=10.

### 2017-07-04 Papers/ViscousInstabilities/article_figure1.tex
updates

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.7\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{2.5cm} (a) pressure at t=0s \hspace{5.cm} (b) t=0.87s \hspace{2.75cm} (c) t=3.54s}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
      \includegraphics[width=.65\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
\vspace{0.cm}
\hbox{ \hspace{1.cm} (d) t=8.86s \hspace{3.0cm} (e) t=12.41s   \hspace{4.0cm} (f) t=17.95s}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $47500$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN3}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b}
\hspace{0.5cm}      
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D1600b}}
\vspace{0.cm}
\hbox{\hspace{5.cm} (a) t=0.27s \hspace{8.cm} (b) t=0.94s }
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D2700b}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D4000b}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D7000b}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (c) t=1.32s \hspace{4.5cm} (d) t=1.70s \hspace{4.5cm} (e)t=2.31s}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=150, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage

\begin{comment}

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{3.cm} (e) t=XXX\red{(???)}}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $47000$ \PN[1]{2} triangular elements. The pressure and saturation range of values are the same like the  case in fig.\ref{fig:homoheleshaw_VN3}.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-1cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation. The domain contains 26313 \PN[1]{2} element-pairs.}
\label{fig:HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage
\end{comment}

@@

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.7\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{2.5cm} (a) pressure at t=0s \hspace{5.cm} (b) t=0.87s \hspace{2.75cm} (c) t=3.54s}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
      \includegraphics[width=.65\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
\vspace{0.cm}
\hbox{ \hspace{1.cm} (d) t=8.86s \hspace{3.0cm} (e) t=12.41s   \hspace{4.0cm} (f) t=17.95s}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN3}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b}
\hspace{0.5cm}      
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D1600b}}
\vspace{0.cm}
\hbox{\hspace{5.cm} (a) t=0.27s \hspace{8.cm} (b) t=0.94s }
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D2700b}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D4000b}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D7000b}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (c) t=1.32s \hspace{4.5cm} (d) t=1.70s \hspace{4.5cm} (e)t=2.31s}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=150, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN150}
\end{figure}
\end{landscape}
\clearpage

@@

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability} }
      \hbox{\hspace{1.0cm} (a) permeability map }}
\caption{3D channel flow \red{FIGS AND COMMENTS TO BE ADDED AS SOON AS THE SIMULATION FINISHES}. The domain contains 243056 \PN[1]{1} element-pairs.}
\label{fig:3DChannel_PermMesh}
\end{figure}
\clearpage
